---
title: "R Notebook"
output:
  bookdown::word_document2: 
    fig_caption: TRUE
  html_document:
    df_print: paged
  pdf_document: default
---

```{r echo=FALSE, message = FALSE,warning=FALSE}
library(knitr)
library(magrittr)
options(kableExtra.auto_format = FALSE)
```

```{r include=F}
# cits_tb <-rorcid::works(rorcid::as.orcid("0000-0001-7407-9194"))
# cits_tb %>% dplyr::select(title.title.value,`publication-date.year.value`,`journal-title.value`) %>% kableExtra::kable()
accepted_tb <- tibble::tibble(Title = c("Identification and Management of Psoriasis Associated Co-MorbidiTy: The IMPACT Research Programme^"),
                              Author = c("L Cordingley, PA Nelson, L Davies, D Ashcroft, C Bundy, C Chew-Graham, A Chisholm, J Elvidge, M Hamilton, R Hilton, K Kane, C Keyworth, A Littlewood, K Lovell, M Lunt, H McAteer, D Ntais, R Parisi, C Pearce, M Rutter, D Symmons, H Young  & CEM Griffiths"),
                              Journal = c("Programme Grants Appl Res"),
                              Year = 2020,
                              Citations = 0)
published_tb <- scholar::get_publications("t1ZHrCoAAAAJ") %>%
  tibble::as_tibble() %>%
  dplyr::filter(!pubid %in% c("IjCSPb-OGe4C","0EnyYjriUFMC","kNdYIx-mwKoC","KlAtU1dfN6UC","3fE2CSJIrl8C","5nxA0vEk-isC","2osOgNQ5qMEC","Y0pCki6q_DkC")) %>%
  dplyr::arrange(dplyr::desc(year)) %>%
  dplyr::select(title,author,journal,year,cites) %>%
  dplyr::rename(Title = title, Author = author, Journal = journal, Year = year, Citations = cites) %>%
  dplyr::filter(Title != "Developing a youth suicide prevention strategy for Tasmania: A review of the literature")
pr_tb <- dplyr::bind_rows(accepted_tb,published_tb)
```

```{r include=F}
non_pr_tb <- read.csv("Non_PR_Pubs.csv")
```

```{r include=F}
presentations_tb <- read.csv("Presentations.csv")
```

```{r include=F}
grants_tb <- read.csv("Grants.csv")
```

# MATTHEW HAMILTON 
orcid.org/0000-0001-7407-9194

# EDUCATION & QUALIFICATIONS

MSc – Health Economics (first class grade average), National University of Ireland Galway, Ireland (2013).
BBS – Economics & Accountancy with French, University of Limerick, Ireland (1997). 

# EMPLOYMENT & APPOINTMENTS

## Senior Policy Analyst / Lecturer in Health Economics / Lead – Health Economics Work Stream at Orygen, Australia
April 2015 – Present (5 years – Full-time)
##Honorary Senior Lecturer in Population Health, Health Services Research and Primary Care, School of Health Sciences, University of Manchester.
October 2018 – Present (1 year and 6 months – Honorary)
##Research Associate - Health Economics at University of Manchester, UK
October 2013 – March 2015 (1 year and 6 months – Full-time)
##Consultant / Course Director- Health Economics and Policy at Leading Edge Group, Ireland
April 2012 - Present (7 years 6 months – Part-time / consultancy)
##Research and Development Manager - Preventative Mental Health at UnitingCare NSW.ACT, Australia
July 2013 - September 2013 (3 months – Consultancy Contract - Full-time)
##Senior Policy Adviser at Orygen Youth Health Research Centre, Australia
March 2010 - March 2012 (2 years – Full-time)
##Teacher / Consultant / Researcher at Fundacion Rose, Trust for the Americas and Footprint Travel Guide, Central America and Caribbean
January 2008 - March 2010 (2 years 2 months – Full-time and part-time / consultancy)
##Portfolio Manager - Mental Health at The One Foundation, Ireland
September 2005 - August 2007 (2 years – Full-time)
##Policy Analyst at Orygen Youth Health Research Centre, Australia
January 2004 - June 2005 (1 year 6 months – Full-time and part-time)
##Head of Policy, Research & Communications at The Wheel, Ireland
September 2001 - September 2003 (2 years – Full-time)
##Co-Founder / Director of Finance and Operations at Silver Apples Media, Ireland
October 1998 - March 2001 (2 years 6 months – Full-time)

#OUTPUTS

##Publications and grant income
Tables 1-4 summarise 18 published works (3 as first author) in peer reviewed journals from the last five years, a selection of 10 other publications from the last decade, 22 presentations from the last six years and three grant successes from the last three years respectively. Additionally, the following work in progress is anticipated to be completed to at least submission for review by the end of June this year:
•	3 papers (one of which I lead), 14 open source code libraries (13 of which I am principal author) and 3 open data packs (all, principal creator) as outputs of a project for which I am Principal Investigator;
•	Six other papers for which I am a contributing co-author, two of which are under review with another an invited contribution.


##Teaching
In addition to one year spent working as a high school teacher, I have the following experience as Course Director and/or Workshop Facilitator:
•	Understanding and Applying Health Economic Tools and Techniques, Online Course, Leading Edge Group, 2015-Present.
•	Health economics: evidence, outcomes and efficiency. Toronto, Canada, June 2014.
•	Using health economic evidence to enhance hospital pharmacy outcomes. Dublin, Ireland, May 2014.
•	Become your own hero – decision making for better health, work and life. Antigua and Barbuda, Dominica, Grenada, St.Kitts and Nevis, St. Vincent and the Grenadines and St. Lucia, 2009.

Additionally, I have contributed content as Lecturer or Assessor to the following University programs:
•	Public Health Policy Guest Lecture, Public Health Bachelor Degree, Australian Catholic University, 2015
•	Health Economic Evaluation Lectures, Epidemiology Module, Masters of Clinical Rheumatology, University of Manchester 2015.
•	Health Economic Evaluation Module, Masters of Public Health, University of Manchester 2014.



```{r echo=F, warning=F}
pr_tb %>%
    kableExtra::kable(caption = "Accepted and published peer-reviewed work") %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
  kableExtra::footnote(general = "^ = In Press" )
```

```{r echo=F, warning=F}
non_pr_tb %>%
    kableExtra::kable(caption = "Published non-peer-reviewed work") %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
  kableExtra::footnote(general = "^ = In Press" )
```

```{r echo=F, warning=F}
presentations_tb %>%
    kableExtra::kable(caption = "Presentations at conferences, symposia, seminars and other events") %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
  kableExtra::footnote(general = "^ = In Press" )
```

```{r echo=F, warning=F}
grants_tb %>%
    kableExtra::kable(caption = "Grant income") %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
  kableExtra::footnote(general = "^ = In Press" )
```
